### 2023-02-22 paper.tex
Added AR and Conclusion

        (p3)

@@

>>>>

        The concept of programming robots by using AR is another new approach to programming robots.
        The general idea of AR is to integrate additional information into the real world. In our specific case this could be an overlay of the robot adding methods to control the robot.
        The authors of \cite{p3} proposed a concept of how this could be done using a HoloLense from Microsoft.
        For example did they add the ability to specify a pickup and a place location. This allows for an automatic path generation. The path then gets visualized in the HoloLense display. The user can edit this path by gestures and the movement of the robot can be simulated.
        If the user is satisfied with the path the robot can be instructed to execute the path with a voice command. %cite this?
        \cite[p. 2]{p3}

        They found that the time needed to teach a robot using their AR based method was significantly shorter than with the traditional kinesthetic teaching approach. 
        They also found that the average completion rate was significantly higher in a task containing movements where the path has to be made out of a high amount of distinct points, for example a sin. Using the AR method led to users placing more points on the path as it was easier to do so, resulting in better results in the sin movement.
        \cite[pp. 4-5]{p3}

@@

\section{Conclusion}

    Generally programming robots is still a complex task and can be done in many ways. 
    In the past the programming of robots was done by experts who had to know the complex physics of the robot and the environment. Modern concepts nowadays tend to simplify this task by adding abstraction layers or high level methods like AR or VR to the programming workflow. This allows for a more intuitive programming workflow and makes it easier for non experts to program robots. Modern concepts also help to reduce costs and time needed to program a robot, making the usage of robotic more accessible for small- and medium-sized companies.
    Nevertheless, there are still many challenges to overcome before programming robots becomes a simple task for everyone. For example the usage of AR and VR is still limited to a few experimental environments and the usage of semantic programming is still in its infancy. Would these concepts improve in functionality and usability and become more widespread, they could be a big step towards a more accessible programming of robots.
